%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}

% Example
%
% \cventry
%   {Degree}
%   {Institution}
%   {Location}
%   {Dates}
%   {
%     \begin{cvitems}
%       \item{Description}
%     \end{cvitems}
%   }
%

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
\cventry
  {Ph.D. in Physical Chemistry} % Degree
    {University Of Oregon} % Institution
    {Eugene, Oregon} % Location
    {Sep. 2012 - Exp. Sep. 2017} % Date(s)
    {
      \begin{cvitems}
        \item{Promising Scholar Award (\textbf{2012}). Award offered to a select group of incoming graduate students in recognition of their academic excellence in expectation of the unique perspectives they will bring to campus.}
        \item{Molecular Biology Biophysics Traning Grant (\textbf{2014--16}). NIH training grant awarded yearly through the University of Oregon’s Institute of Molecular Biology. The objective is this award being to facilitate training to prepare graduate students to work on important problems in molecular biology and biophysics. This is accomplished by collaboration between multifaceted research programs.}
      \end{cvitems}
    }
  \cventry
     {B.S. in Chemistry with a minor in Mathematics} % Degree
     {St. Edward's University} % Institution
     {Austin, Texas} % Location
     {Aug. 2008 - May. 2012} % Date(s)
     {
       \begin{cvitems} % Description(s) bullet points
         \item{Welch Research Grant (\textbf{2010--11}). Given to Chemistry \& Biochemistry students who perform novel research.}
         \item{Brother Daniel Lynch Research Award (\textbf{2011}). Provides support to senior students engaged in research projects who excel in academics and community service.}
         \item{President's Scholar Award (\textbf{2008--12}). For academic merit reviewed recurrently every semester.}
       \end{cvitems}
     }
\end{cventries}
