%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Presentation \& Workshops}

% Example
%
% \cventry
%   {Role/Title}
%   {Event}
%   {Location}
%   {Dates}
%   {
%     \begin{cvitems}
%       \item{Description}
%     \end{cvitems}
%   }
%

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  \cventry
    {Chiral Pathways in DNA dinucleotides using gradient optimized refinement along metastable borders} % Role
    {American Physical Society: National Meeting} % Event
    {New Orleans, Louisiana} % Location
    {Mar. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item{Presented talk on novel method for refining of Markov State Models. The method used underlying probability distribution to correct undersampling while retaining crisp boundaries.}
      \end{cvitems}
    }

  \cventry
    {CECAM Macromolecular Simulation Software Workshop}
    {Centre Europ{\'e}en de Calcul Atomique et Mol{\'e}culaire}
    {J{\"u}lich, Germany}
    {Oct. 2015}
    {
      \begin{cvitems}
        \item{“Hackathon” workshop with the aim of tackling the most challenging problems within macromolecular modeling, particularly those relating to how the capabilities of and opportunities presented by future generations of massive heterogeneous, computational resources can best be leveraged in this domain of science.}
        \item{Travel expenses were funded by travel fellowship awarded to promising US candidates.}
      \end{cvitems}
    }

  \cventry
    {Analyzing Small DNA Constructs via a Chromophore Model within the Point Dipole Approximation.} % Role
    {Biophysical Society: National Meeting} % Event
    {Baltimore, Maryland} % Location
    {Mar. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item{Presented poster on ensemble model to predict the Circular Dichroism spectra of small oligonucleotide constructs employing a classical point dipole approximation.}
      \end{cvitems}
    }

  \cventry
    {Coarse-Graining and Multiscale Modeling in Complex Chemical Systems}
    {American Chemical Society: National Meeting}
    {Indianapolis, Indiana}
    {Sep. 2013}
    {
      \begin{cvitems}
        \item{Attended conference for development of academic and research pursuits.}
        \item{Travel expenses were funded by a NSF Phase 1 Center for Chemical Innovation. Fellowship awarded to underrepresented minorities students in the STEM field.}
      \end{cvitems}
    }

  \cventry
    {Acetylenic inhibitors of ADAM10 and ADAM17: In silico analysis of potency and selectivity} % Role
    {American Chemical Society: Southwest Regional Meeting} % Event
    {New Orleans, Louisiana} % Location
    {Sep. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item{Presented talk on comparative study on binding potency and selectivity effects for inhibitors targeting TACE protein family.}
      \end{cvitems}
    }
\end{cventries}
