%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Research Experience}

% \begin{cventries}
%     \cventry
%         {Organization}
%         {Institution}
%         {Location}
%         {Date(s)}
%         {Description}
% \end{cventries}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  \cventry
    {Marina Guenza Lab}
    {University of Oregon}
    {Eugene, Oregon}
    {Sep. 2012 - Sep. 2017}
    {
      \begin{cvitems}
        \item{Developed ``Gradient Adaptive Decomposition'' (\emph{GRAD}) method to refine kinetic states by optimizing decision boundaries along gradient of the energetic distribution. Reproduced decomposition, label assignment, and transition timescales by refining undersampled Markov model.}
        \item{Modeled the conformational dynamics of DNA slow barrier crossing within stacking transitions, assessing chiral pathways involved in thermally induced breathing fluctuations critical in protein recognition.}
        \item{Developed Python API and Fortran+F2PY backend for \emph{GRAD} method and developed Python API to Langevin Equation for Protein Dynamics (\emph{LE4PD}) for the analysis of large all atom molecular dynamics datasets.}
        \item{Simulated several microsecond molecular dynamics simulations of various biological molecule on Extreme Scientific and Engineering Discovery Environment (XSEDE).}
    \end{cvitems}
    }

  \cventry
    {Eamonn Healy Lab}
    {St. Edward's University}
    {Austin, Texas}
    {Jan. 2009 - Jun. 2012}
    {
      \begin{cvitems}
        \item{Analyzed structural homogeneity of ADAM10 and ADAM17 to study drug potency and selectivity. The ADAM family is a class of enzymes largely linked to inflammatory response in pathologies such as rheumatoid arthritis and metastasis in cancers.}
        \item{Designed novel inhibitors that selectively targeting ADAM17 while maximizing potency and reducing the selectivity in ADAM10 and thereby reducing liklihood of side effects.}
        \item{Performed docking studies within Accelrys Discovery Studio to structurally evaluate novel acetylenic based inhibitors and score the resulting ``docked'' structures.}
      \end{cvitems}
    }
\end{cventries}
