%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Teaching Experience}

% \begin{cventries}
%     \cventry
%         {Job title}
%         {Organization}
%         {Location}
%         {Date(s)}
%         {Description}
% \end{cventries}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  \cventry
    {Lab Teaching Assistant}
    {St. Edward's University Department of Chemistry}
    {Austin, Texas}
    {Aug. 2010 - Jun. 2012}
    {
      \begin{cvitems}
        \item{Assisted in laboratory course work for General Chemistry, Organic Chemistry I \& II, and Biochemistry.}
        \item{Responsibilities included giving lab lectures, assisting in desiging lab coursework, and preparing and standardizing stock reagent.}
      \end{cvitems}
    }

  \cventry
    {Supplemental Instructor}
    {St. Edward's University Academic Success Center}
    {Austin, Texas}
    {Aug. 2010 - Jun. 2012}
    {
      \begin{cvitems}
        \item{Assisted in course work in General Chemistry, Organic Chemistry I \& II, Analytical Chemistry, and Biochemistry.}
        \item{Expectations for the position involved holding office hours and leading two weekly group study lectures as a supplement to to coincide with course work.}
      \end{cvitems}
    }

  \cventry
    {Graduate Teaching Fellow}
    {University of Oregon Department of Chemistry}
    {Eugene, Oregon}
    {Sep. 2012 - Sep. 2014}
    {
      \begin{cvitems}
        \item{Assisted in laboratory course work for General Chemistry I, II, \& III.}
        \item{Work expectations involved weekly office hours, assisting in theory based lectures, leading and lecturing course experiments, assisting in course examinations, and grading lab coursework.}
      \end{cvitems}
    }

  \cventry
    {Undergraduate Research Mentor}
    {University of Oregon Department}
    {Eugene, Oregon}
    {Sep. 2012 - Sep. 2014}
    {
      \begin{cvitems}
        \item{Trained and mentored undergraduates in research and computational methods.}
        \item{Students were trained to run Molecular Dynamics (MD) simulations using Gromacs.}
        \item{Visualization used PyMol and Visual Molecular Dynamics software.}
        \item{Additional requirements for mentorship involved teaching students to use Linux operating systems, giving a 2 hour course on Research Ethics, and conducting weekly research review sessions to help students develop proper research methods.}
      \end{cvitems}
    }

  \cventry
    {Nonequilibrium Statistical Mechanics}
    {University of Oregon Department of Chemistry}
    {Eugene, Oregon}
    {Sep. 2016}
    {
      \begin{cvitems}
        \item{Week long lecture series on non equilibrium statistical mechanics focused on applications Markov State Models (MSM) of biological macromolecules.}
        \item{The series presented up to date theory, development of the field, and provided a hands-on learning module using the Python and PyEMMA software package.}
        \item{Students built MSMs for protein folding simulations.}
      \end{cvitems}
    }
\end{cventries}
